decompr: GVC decomposition in R

### 2015-02-03 draft.Rnw
conclusion plus time element in intro

@@

@@

% Baast, enter part on how the package is flexible and can be adapted

@@

>>>>

Trade flow analysis often involves studying development of a certain variable (set) over time, thus taking the panel form.
However, no existing trade flow analysis explicitly exploints the time dimsion, making the analysis effectively a repeated cross-section.
As a design decision, the time dimension is therefore not implemented in the package itself.
In stead, we provide examples of how the repeated analysis can be easily implemented using decompr.

@@

\begin{sidewaystable}
\scriptsize

\bigskip \bigskip \bigskip

@@

We have designed the package using a modular structure, with an additional user interface function for increased ease of use.
The modulare structure enables users to break the computationally intensive analysis process down into several steps.
Furthermore, the modular structure enables user and other developers to build on top of basic data structures which are creaed by the \textbf{load\_tables\_vectors} function when implementing other decompositions or analyses.
However, a wrapper function (\textbf{decomp}) is also provided, which combines the use of the atomic functions into one.
Lastly, in addition to the \textbf{decompr} function, we provide a Rcmdr plugin, which allows the user to perform the analytical process using a GUI (Grapical User Interface).

@@

\vspace{\stretch{1}}

\section*{Colophon}
This paper was written in a combination of R and LaTeX (LuaLaTeX) using Sweave formatting and combined using knitr.
